---
title: "Pindograma Polls Database Builder"
author: "Daniel T. Ferreira"

output: html_document
---

<!--
This file is (c) 2020 CincoNoveSeis Jornalismo Ltda.
It is licensed under the GNU General Public License, version 3.
-->

Let's start with the libraries we need:

```{r}
library(purrr)
library(tidyr)
library(dplyr)
library(readr)
library(stringi)
library(stringr)
library(lubridate)
library(mgsub)
library(sqldf)
library(cepespR)

options('sqldf.dll' = '/Users/Daniel/Downloads/sqlite/spellfix.so')

Rcpp::sourceCpp('src/wordmatch.cpp')
source('polling_utils.R')
source('poll_to_candidate_matcher.R')
```

Then, let's download data about all candidates using the Cepesp API:

```{r}
years_1 = c(2012, 2016)
positions_1 = c('Vereador', 'Prefeito')

years_2 = c(2014, 2018)
positions_2 = c('Deputado Estadual', 'Deputado Federal', 'Senador', 'Governador',
                'Presidente')

cands_1 = map_dfr(years_1, function(y) {
  map_dfr(positions_1, function(p) {
    get_candidates(y, p, columns_list = list(
      'ANO_ELEICAO', 'NUM_TURNO', 'SIGLA_UF', 'SIGLA_UE', 'DESCRICAO_UE',
      'CODIGO_CARGO', 'NOME_CANDIDATO', 'NOME_URNA_CANDIDATO', 'NUMERO_CANDIDATO'
    ), cache = T)
  })
})

cands_2 = map_dfr(years_2, function(y) {
  map_dfr(positions_2, function(p) {
    get_candidates(y, p, columns_list = list(
      'ANO_ELEICAO', 'NUM_TURNO', 'SIGLA_UF', 'SIGLA_UE', 'DESCRICAO_UE',
      'CODIGO_CARGO', 'NOME_CANDIDATO', 'NOME_URNA_CANDIDATO', 'NUMERO_CANDIDATO'
    ), cache = T)
  })
})

cands_orig = tibble(bind_rows(cands_1, cands_2))
rm(cands_1, cands_2)

cands = cands_orig %>%
  mutate(NOME_CANDIDATO = normalize_cand(NOME_CANDIDATO)) %>%
  mutate(NOME_URNA_CANDIDATO = normalize_cand(NOME_URNA_CANDIDATO)) %>%
  mutate(NOME_URNA_CANDIDATO = recode(NOME_URNA_CANDIDATO,
    `ELMANO O VEIN TRABALHADOR` = 'ELMANO FERRER',
    `DR. PESSOA (DR. ZEZIM)` = 'DR. PESSOA'
  )) %>%
  mutate(CODIGO_CARGO = ifelse(CODIGO_CARGO == 8, 7, CODIGO_CARGO))

rm(cands_orig)
```

Now, let's take a last stab at removing duplicates and unwanted scenarios from
Pindograma's two datasets:

```{r}
manual_tse = read_csv('output/raw_pindograma_manual_polls.csv') %>%
  distinct(scenario_id, candidate, result, .keep_all = T) %>%
  group_by(scenario_id) %>%
  filter(n_distinct(candidate) == n()) %>%
  mutate(scenario_count = n()) %>%
  ungroup() %>%
  group_by(NR_IDENTIFICACAO_PESQUISA, estimulada, CD_CARGO, vv, SG_UE, NR_CNPJ_EMPRESA) %>%
  mutate(multiple_scenarios = n_distinct(scenario_id) > 1) %>%
  filter(scenario_count == max(scenario_count)) %>%
  ungroup() %>%
  select(-scenario_count) %>%
  mutate(candidate_without_title = normalize_cand_rm_titles(candidate))

pdf_polls = read_csv('output/raw_pindograma_automatic_polls.csv') %>%
  filter(!grepl('EM BRANCO|NULO|NENHUM|BASE|TOTAL|OUTROS|OUTRAS|NAO SABE|NAO RESPOND|RECUSA|NS\\/NR|CITOU OUTRO', candidate)) %>%
  group_by(NR_IDENTIFICACAO_PESQUISA, estimulada, CD_CARGO, scenario_id) %>%
  filter(n_distinct(candidate) == n()) %>%
  mutate(scenario_count = n()) %>%
  ungroup() %>%
  group_by(NR_IDENTIFICACAO_PESQUISA, estimulada, CD_CARGO, NR_CNPJ_EMPRESA) %>%
  mutate(multiple_scenarios = n_distinct(scenario_id) > 1) %>%
  filter(scenario_count == max(scenario_count)) %>%
  ungroup() %>%
  select(-scenario_count) %>%
  mutate(candidate_without_title = normalize_cand_rm_titles(candidate))
```

And now, let's match everything with a single line:

```{r}
manual_matches = match_polls_with_candidates(manual_tse)
```

Now, it's time to apply everything we've done with the manual dataset so far to
the polls that are parsed automatically from pollster PDFs:

```{r}
pdf_matches = match_polls_with_candidates(pdf_polls, F)
```

Let's do the same with the Poder360 polls:

```{r}
p3_polls = read_csv('output/pindograma_poder360_polls.csv')
p3_matched = match_polls_with_candidates(p3_polls)
```

Now, let's join everything. We take the following order of precedence:

1. Polls extracted automatically from PDFs;
2. Polls extracted manually by Pindograma;
3. Polls from Poder360.

```{r}
manual_matches_without_pdf = manual_matches %>%
  anti_join(pdf_matches, by = c(
    'NR_IDENTIFICACAO_PESQUISA',
    'SG_UE',
    'NR_CNPJ_EMPRESA'
  ))

polls = bind_rows(pdf_matches, manual_matches_without_pdf)

p3_without_pindograma_polls = p3_matched %>%
  anti_join(polls, by = c(
    'NR_IDENTIFICACAO_PESQUISA' = 'NR_IDENTIFICACAO_PESQUISA',
    'NR_CNPJ_EMPRESA' = 'NR_CNPJ_EMPRESA',
    'SG_UE' = 'SG_UE',
    'CD_CARGO' = 'CD_CARGO',
    'estimulada' = 'estimulada',
    'vv' = 'vv'
  ))

ambito = read_csv2('data/manual-data/ambito.csv') %>%
  select(-DS_METODOLOGIA_PESQUISA, -DS_PLANO_AMOSTRAL, -DS_DADO_MUNICIPIO) %>%
  mutate(SG_UE = ifelse(LOCAL == 'CID', CID_UE, LOCAL)) %>%
  mutate(SG_UE = ifelse(nchar(SG_UE) != 2, str_pad(SG_UE, 5, pad = '0'), SG_UE)) %>%
  mutate(id = str_replace_all(X1, '[\\-\\/]', '')) %>%
  rename(polled_UE = SG_UE) %>%
  distinct(id, .keep_all = T)

company_names = read_csv('data/manual-data/nomes_empresas.csv')

all_polls__ = bind_rows(
  polls,
  p3_without_pindograma_polls
) %>%
  distinct(year, NR_IDENTIFICACAO_PESQUISA, NR_CNPJ_EMPRESA, SG_UE, CD_CARGO,
           estimulada, NUMERO_CANDIDATO, result, DT_FIM_PESQUISA, vv, turno,
           is_fluxo, is_phone, self_hired, QT_ENTREVISTADOS, main_source, source, scenario_id, is_complete) %>%
  left_join(ambito, by = c('NR_IDENTIFICACAO_PESQUISA' = 'id')) %>%
  mutate(polled_UE = ifelse(!is.na(polled_UE), polled_UE, SG_UE)) %>%
  select(-X1, -LOCAL, -CIDNAME, -CID_UE) %>%
  mutate(state = case_when(
    polled_UE == 'BR' ~ 'BR',
    nchar(polled_UE) == 2 ~ polled_UE,
    T ~ str_sub(NR_IDENTIFICACAO_PESQUISA, start = 1, end = 2)
  ))

all_polls_ = all_polls__ %>%
  group_by(NR_IDENTIFICACAO_PESQUISA, NR_CNPJ_EMPRESA, SG_UE, polled_UE, estimulada, CD_CARGO, vv, scenario_id) %>%
  mutate(group_digest = fastdigest(cur_data() %>% arrange(NUMERO_CANDIDATO) %>% select(NUMERO_CANDIDATO, result))) %>%
  ungroup() %>%
  group_by(NR_IDENTIFICACAO_PESQUISA, NR_CNPJ_EMPRESA, SG_UE, polled_UE, estimulada, CD_CARGO, vv, group_digest) %>%
  filter(scenario_id == first(scenario_id)) %>%
  ungroup()

all_polls = all_polls_ %>%
  mutate(company_id = case_when(
    NR_CNPJ_EMPRESA %in% c('24776969000117', '07742623000189', '67662494000140', '14931054000185', '26195312000191') ~ 'REALIDADE',
    NR_CNPJ_EMPRESA %in% c('23254436000102', '00852438000106', '00852501000104') ~ 'VOX POPULI',
    NR_CNPJ_EMPRESA %in% c('05939922000263', '32208779000121') ~ 'GERP',
    NR_CNPJ_EMPRESA %in% c('10828442000184', '22198794000182') ~ 'MULTIPLA',
    NR_CNPJ_EMPRESA %in% c('17070395000100', '06154093000195') ~ 'MULTIDADOS',
    NR_CNPJ_EMPRESA %in% c('09656847000101', '09283689000183') ~ 'PROMIDIA',
    NR_CNPJ_EMPRESA %in% c('03622028000159', '39795414000190') ~ 'FUTURA',
    NR_CNPJ_EMPRESA %in% c('26968293000199', '11785871000184') ~ 'RANKING',
    NR_CNPJ_EMPRESA %in% c('57541377000175', '16623147000178') ~ 'DGABC',
    NR_CNPJ_EMPRESA %in% c('01077145000153', '10575983000148') ~ 'DATAMETRICA',
    NR_CNPJ_EMPRESA %in% c('13776203000116', '12784563000105') ~ 'ARBEIT',
    T ~ NR_CNPJ_EMPRESA
  )) %>%
  left_join(company_names, 'company_id')
```

Finally, let's print it:

```{r}
all_polls %>%
  write.csv('output/pindograma_polls.csv', row.names = F)
```