---
title: "Pindograma Selected Polls Exporter"
author: "Daniel T. Ferreira"

output: html_document
---

<!--
This file is (c) 2020 CincoNoveSeis Jornalismo Ltda.
It is licensed under the GNU General Public License, version 3.
-->

Let's start by getting the votes:

```{r}
pvotes = get_votes(
  year = '2016, 2012',
  position = 'Prefeito',
  blank_votes = T,
  null_votes = T,
  regional_aggregation = 'Municipality',
  columns_list = list('ANO_ELEICAO', 'SIGLA_UE', 'CODIGO_CARGO', 'NUMERO_CANDIDATO', 'QTDE_VOTOS', 'NUM_TURNO'),
  cache = T) %>%
    tibble()

gov_votes_city = get_votes(
  year = '2018, 2014',
  position = 'Governor',
  blank_votes = T,
  null_votes = T,
  regional_aggregation = 'Municipality',
  columns_list = list('ANO_ELEICAO', 'COD_MUN_TSE', 'CODIGO_CARGO', 'NUMERO_CANDIDATO', 'QTDE_VOTOS', 'NUM_TURNO'),
  cache = T) %>%
    rename(SIGLA_UE = COD_MUN_TSE) %>%
    tibble()

gov_votes_state = get_votes(
  year = '2018, 2014',
  position = 'Governor',
  blank_votes = T,
  null_votes = T,
  columns_list = list('ANO_ELEICAO', 'UF', 'CODIGO_CARGO', 'NUMERO_CANDIDATO', 'QTDE_VOTOS', 'NUM_TURNO'),
  regional_aggregation = 'State',
  cache = T) %>%
    tibble() %>%
    rename(SIGLA_UE = UF)

pres_votes_state = get_votes(
  year = '2018, 2014',
  position = 'President',
  blank_votes = T,
  null_votes = T,
  columns_list = list('ANO_ELEICAO', 'UF', 'CODIGO_CARGO', 'NUMERO_CANDIDATO', 'QTDE_VOTOS', 'NUM_TURNO'),
  regional_aggregation = 'State',
  cache = T) %>%
    tibble() %>%
    rename(SIGLA_UE = UF)

pres_votes_natl = get_votes(
  year = "2018, 2014",
  position = 'Presidente',
  blank_votes = T,
  null_votes = T,
  regional_aggregation = 'Brazil',
  columns_list = list('ANO_ELEICAO', 'CODIGO_CARGO', 'NUMERO_CANDIDATO', 'QTDE_VOTOS', 'NUM_TURNO'),
  cache = T) %>%
    tibble() %>%
    mutate(SIGLA_UE = 'BR')

votes = bind_rows(pvotes, pres_votes_state, pres_votes_natl, gov_votes_state, gov_votes_city) %>%
  filter(NUMERO_CANDIDATO != 95 & NUMERO_CANDIDATO != 96) %>%
  group_by(ANO_ELEICAO, NUM_TURNO, SIGLA_UE, CODIGO_CARGO) %>%
  mutate(qtde_all_valid = sum(QTDE_VOTOS)) %>%
  arrange(desc(QTDE_VOTOS), .by_group = T) %>%
  ungroup()

rm(pvotes, pres_votes_state, pres_votes_natl, gov_votes_state, gov_votes_city)
```

Now, let's clean our polls by removing all sorts of bizarre things that we got
in our database.

```{r}
cleaned_polls = all_polls %>%
  filter(CD_CARGO %in% c(1, 3, 11)) %>%
  group_by(NR_IDENTIFICACAO_PESQUISA, NR_CNPJ_EMPRESA, SG_UE, estimulada, CD_CARGO, vv, scenario_id) %>%
  mutate(unique_poll = cur_group_id()) %>%
  ungroup() %>%
  group_by(unique_poll) %>%
  filter(all(result < 100)) %>%
  ungroup() %>%
  group_by(unique_poll, NUMERO_CANDIDATO) %>%
  filter(all(n() == 1)) %>% # TODO: Manual candidate matching
  ungroup() %>%
  filter(result >= 1)

no_vv_polls = cleaned_polls %>%
  filter(!vv)
```

Now, let's get a dataset of "early polls" and one of "late polls". Early polls
are the espontânea polls made before the candidates are officially registered
with the TSE. Late polls are estimulada polls that come after the candidates
are officially registered (though if a poll only releases espontânea data,
we will use it as if it were an estimulada poll).

In both cases, we remove polls with more than one scenario. This makes sense,
since after the official candidate list is available, we don't need scenarios;
and espontânea polls don't have scenarios by definition. Most of the times, these
multiple scenarios exist because of badly inputted data.

There is one exception to this rule -- the races where a candidate is
registered, but where there is significant doubt about whether that candidate
will be able to run. This was the case in the 2018 presidential election.
These cases are "special" and marked as such.

Alas -- these are the polls that will feed our polling average.

```{r}
get_final_poll_list = function(p) {
  p %>%
    group_by(NR_IDENTIFICACAO_PESQUISA, NR_CNPJ_EMPRESA, SG_UE, polled_UE, estimulada, CD_CARGO, vv) %>%
    filter(n_distinct(scenario_id) == 1) %>%
    ungroup() %>%
    inner_join(votes, by = c(
      'year' = 'ANO_ELEICAO',
      'turno' = 'NUM_TURNO',
      'polled_UE' = 'SIGLA_UE',
      'CD_CARGO' = 'CODIGO_CARGO',
      'NUMERO_CANDIDATO' = 'NUMERO_CANDIDATO'
    )) %>%
    left_join(df_for_merge %>% select(NR_CNPJ_EMPRESA, NR_IDENTIFICACAO_PESQUISA,
                                      partisan, DT_INICIO_PESQUISA, hirer,
                                      confidence_interval_final, error_final),
              by = c('NR_CNPJ_EMPRESA' = 'NR_CNPJ_EMPRESA', 'NR_IDENTIFICACAO_PESQUISA' = 'NR_IDENTIFICACAO_PESQUISA')) %>%
    mutate(non_partisan = !partisan & !self_hired) %>%
    group_by(year, turno,
             NR_IDENTIFICACAO_PESQUISA, NR_CNPJ_EMPRESA, SG_UE, polled_UE, CD_CARGO, estimulada, vv, scenario_id, source,
             DT_INICIO_PESQUISA, DT_FIM_PESQUISA, self_hired, is_phone, is_fluxo, QT_ENTREVISTADOS,
             non_partisan, first_round_date, second_round_date, is_complete, state,
             hirer, confidence_interval_final, error_final) %>%
    mutate(valid_result = ifelse(vv, result, result / sum(result) * 100)) %>%
    mutate(pct = QTDE_VOTOS / sum(QTDE_VOTOS) * 100) %>%
    filter(sum(QTDE_VOTOS) >= 0.90 * qtde_all_valid) %>%
    mutate(undecided = ifelse(vv, NA, 100 - sum(result))) %>%
    ungroup()
}

early_polls = no_vv_polls %>%
  left_join(election_dates, 'year') %>%
  filter(DT_FIM_PESQUISA <= candidate_registry_date) %>%
  filter(estimulada == 0) %>%
  get_final_poll_list()

late_polls = no_vv_polls %>%
  left_join(election_dates, 'year') %>%
  filter(DT_FIM_PESQUISA > candidate_registry_date) %>%
  group_by(NR_IDENTIFICACAO_PESQUISA, NR_CNPJ_EMPRESA, SG_UE, polled_UE, CD_CARGO, vv) %>%
  filter(n_distinct(estimulada) == 1 | estimulada == 1) %>%
  ungroup() %>%
  get_final_poll_list()

early_polls %>%
  write.csv('output/early_polls.csv', row.names = F)

late_polls %>%
  write.csv('output/late_polls.csv', row.names = F)
```